Study of Intra- and Inter-Job Interference on Torus Networks

### 2016-07-13 submission.tex
change title, add keywords
pass on Abstract

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Study of Intra- and Inter-Job Interference with Different Job Allocations}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{

@@

Network contention between concurrently running jobs on HPC systems 
is a primary cause of performance variability. 
Optimizing job allocation and avoiding network sharing are 
hence crucial to alleviate the potential performance degradation. 
In order to do these effectively, 
an understanding of the interference among the concurrently running jobs, 
their communication patterns, and the network contention are required. 
In this work, we choose three representative HPC applications from 
DOE Design Forward Project and conduct detailed simulations of 
on a Torus network model to analyze both intra- and inter-job interference. 
By scrutinizing the communication behaviors of these applications, 
we identify relationships between these behaviors and 
the possible interference introduced by different job placement policies. 
Our comprehensive analyses in this work illuminate a path 
towards job-communication-pattern-aware HPC resource allocation.

@@

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Study of Intra- and Inter-Job Interference on Torus Networks}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{

@@

Network contention between concurrently running jobs on HPC systems 
is a primary cause of performance variability. 
Optimizing job allocation and avoiding network sharing are 
hence crucial to alleviate the potential performance degradation. 
In order to do so effectively, 
an understanding of the interference among concurrently running jobs, 
their communication patterns, and contention in the network are required. 
In this work, we choose three representative HPC applications from 
the DOE Design Forward Project and conduct detailed simulations  
on a torus network model to analyze both intra- and inter-job interference. 
By scrutinizing the communication behaviors of these applications, 
we identify relationships between these behaviors and 
the possible interference introduced by different job placement policies. 
Our analyses in this work illuminate a path 
towards communication pattern awareness in job placement on HPC systems.

@@

\begin{IEEEkeywords} 
HPC systems, Torus, Interference, Job Placement

\end{IEEEkeywords}
